### 2023-03-15 paper.tex
minor stuff

>>>>

\begin{figure}[h]
    \begin{center}
        \includegraphics[width=\columnwidth]{figures/SFig_parameter_sweep.png}
    \end{center}
    \caption{\small \textbf{Effect of VMR detection parameters on separation of cell types}.\\
    \texttt{(A - B)} Neighbor score obtained after analyzing single-cell methylomes from \citet{kremer_scnmt} (\textbf{A}) or \citettt{luo2017single} (\textbf{B}) with our proposed methods.
    VMRs were detected with \citettt{scbs scan} using various sliding window bandwidths (\citettt{--bandwidth} parameter) or variance thresholds (\citettt{--var-threshold} parameter).
    }
    \label{fig:sweep}
\end{figure}
